### 2023-10-17 README.Rmd
fix itemization

## Contents of the repository
The folders of this repository contain the following:
* `R`: all functions and that the analysis is based on
  - `plot.R`: plotting files 
  - `score.R`: functions to score quantile forecasts (coverage, interval_score, crps by sample)
  - `uqfc.R`: functions to generate quantile forecasts from past errors
  - `uqimf-package.R` some stuff, as this is technically an R package
  - `utils.R` miscellaneous small functions
  - `utils-manuscript.R` miscellaneous small functions for manuscript

>>>>

## Contents of the repository

The folders of this repository contain the following:

- `R`: all functions and that the analysis is based on

  - `plot.R`: plotting files

  - `score.R`: functions to score quantile forecasts (coverage, interval_score, crps by sample)

  - `uqfc.R`: functions to generate quantile forecasts from past errors

  - `uqimf-package.R` some stuff, as this is technically an R package

  - `utils.R` miscellaneous small functions

  - `utils-manuscript.R` miscellaneous small functions for manuscript
